\documentclass[14pt]{beamer}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel}
\usepackage{float}
\usepackage{graphicx}

\newcommand{\tc}[1]{\textcolor{blue}{\textbf{#1}}}

\title{Crimes and Misdemeanors}
\author{Alexandru Fikl}
\date{September 10, 2009}

\begin{document}

\begin{frame}
 \titlepage
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} What’s the best way to treat a jellyfish sting?
    \item[] \tc{A:} Using salt water and calling a doctor.
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} What is the name of the capital city of Thailand?
    \item[] \tc{A:} It's \textbf{Krung Thep} Mahanakhon Amorn Rattanakosin Mahintara Yudthaya
    Mahadilok Pohp Noparat Rajathanee Bureerom Udomrajniwes Mahasatarn Amorn Pimarn
    Avaltarnsatit Sakatattiya Visanukram Prasit.
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} What was the first invention to break the sound barrier?
    \item[] \tc{A:} It was the \textbf{whip}.
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} Who was the first to claim that the earth goes around the sun?
    \item[] \tc{A:} The Greek astronomer \textbf{Aristarchus of Samos} (310 BC)
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} Why shouldn’t you touch a meteorite?
    \item[] \tc{A:} It is very \textbf{cold}.
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\vfill
\begin{center}
    \large
\begin{itemize}[<+-| alert@+>]
    \item[] \tc{Q:} What language was mostly spoken in ancient Rome?
    \item[] \tc{A:} \textbf{Greek.}
\end{itemize}
\end{center}
\vfill
\end{frame}

\begin{frame}
\begin{center}
    {\Large Thank you for your attention!}

    \vfill
    {\huge Questions!?}
    \vfill
    \small Credits to \textbf{Stephen Fry, QI, the internet}.
\end{center}
\end{frame}

\end{document}